\section{Problem Formulation}\label{sec:Formulation}
Let $M$ be a compact Riemannian manifold with volume for $\mu$.  Given a vector field $X \in \mathfrak{X}(M)$ we define the divergence, ${\rm div}(X) \in C^1(M)$ as the unique function such that ${\rm div}(X) \mu = \pounds_X [ \mu ]$.
This induces the advection equation for mass density $\rho \in C^{\infty}(M)$ given by
\[
	\partial_t \rho = - {\rm div}( \rho X ).
\]
In particular, the map $\rho \mapsto - {\rm div}( \rho X)$ is linear in $\rho$, and is the infinitesimal generator of the Perron-Frobenius operator.
We can hope to find a finite-dimensional approximation of this operator, and use the matrix exponential as an approximation of the Perron-Frobenius operator.
This perspective is explored in a number of areas areas \cite{FroylandJungeKoltai2013,FroylandPadberg2009}.
The dual perspective consider the advection equation for a function $f \in C^{\infty}(M)$ given by $\partial_t f = X^i \cdot \partial_i f$ and yields the Koopman operator.
This perpective has also been explored in many contexts \cite{RowleyMezic2009,Mezic2005}

In this paper we will consider a different representation of vector fields, which can be viewed as a mid-point between the generators of the Koopman operator and the Perron-Frobenius operator.
This operator in unitary with respect to a canonical inner product as are the finite dimensional approximations which we will use.
This unitarity allows for convergence proofs and the use of wavelet representations to achieve sufficiently rapid convergence to simulate flows on high dimensional spaces.

\section{Half densities}
A volume form, $\mu \in \left| \bigwedge^n \right|(M)$ can be defined as a non-negative function on the $n$-fold Whitney sum, $TM \oplus \cdots \oplus TM$, such that
\[
	\mu( \alpha v_1, \dots, \alpha v_n) = \alpha^n \mu( v_1, \dots, v_n).
\]
A half density $\Psi \in  \sqrt{ \left| \bigwedge \right|^n(M) }$ is a complex valued function on $TM \oplus \dots \oplus TM$ such that
\[
	\Psi( \alpha v_1, \dots, \alpha v_n) = \alpha^{n/2} \Psi( v_1, \dots, v_n).
\]
We see that there is a natural Hermitian inner-product on $\sqrt{\bigwedge^n(M)}$ given by
\begin{align}
	\langle \Psi_1, \Psi_2 \rangle = \int_M \Psi_1^\dagger \cdot \Psi_2 \label{eq:Hilbert}
\end{align}
where $\Psi_1^\dagger \cdot \Psi_2$ is the complex valued $n$-form obtained by scalar multiplication of $\Psi_1^\dagger$ and $\Psi_2$.
This makes $\sqrt{ \bigwedge^n(M)}$ a pre-Hilbert space, the completion of which we call the \emph{Hilbert space of half-densities}, denoted $\mathcal{H}(M)$ \cite[See Appendix A]{BatesWeinstein1997}
Moreover, given a diffeomophism $\varphi: M \to M$, the pullback of $\Psi \in \sqrt{ \bigwedge^n(M)}$ is
\[
	\varphi^* \Psi( v_1, \cdots , v_n) = \Psi( T\varphi \cdot v_1, \dots, T\varphi \cdot v_n).
\]
This defines the Lie derivative of $\Psi$ with respect to a vector field $X \in \mathfrak{X}(M)$ as the half-density $\pounds_X[ \Psi] := \left. \frac{d}{dt} \right|_{t=0} \varphi_t^* \Psi$ where $\varphi_t$ is the flow of $X$.

\begin{proposition} \label{prop:half_density}
	Let $\Psi(t) \in \sqrt{ \bigwedge^n(M)}$ be a curve in the space of half-densities which satisfies the advection equation
	\[
		\partial_t \Psi + \pounds_X \Psi = 0.
	\]
	Then $\| \Psi(t) \| = \| \Psi(0) \|$.  In other words, the flow of $X$ is a unitary transformation.
\end{proposition}
\begin{proof}
	If $\Psi(t)$ satisfies the advection equation, then $\varphi_t^*\Psi(t) = \Psi(0)$ where $\varphi_t : M \to M$ is the time-$t$ flow map of $X$.  We see that
	\[
		\| \Psi(t) \|^2 = \| (\varphi_t^{-1})^* \Psi(0) \|^2 = \int_M (\varphi_t^{-1})^* \Psi(0)^\dagger \cdot (\varphi_t^{-1})^* \Psi(0).
	\]
	By the change of variables formula the above is equivalent to $\int_M \Psi(0)^\dagger \Psi(0) = \| \Psi(0) \|^2$.
\end{proof}
It is notable that we have not invoked any specific structure of $M$, so that \eqref{eq:Hilbert} is strictly a topological entity.

In any case, on a volume manifold we may consider the half density $\mu^{1/2}$ obtained by taking the square root of $\mu$.
Then any half-density $\Psi$ can be written as the product of a complex valued function $\psi \in C^{\infty}(M ; \mathbb{C})$ such that $\Psi = \psi \cdot \mu^{1/2}$.
We then find that the Lie derivative of $\Psi$ along $X$ is given by
\[
	\pounds_X[ \Psi] = ( \pounds_X[ \psi] + \frac{1}{2} \psi \cdot {\rm div}(X) ) \cdot \mu^{1/2}.
\]
Therefore we can simulate the advection of half densities by solving for the function $\psi$.  This also allows us to simulate densities as follows
\begin{proposition} \label{prop:advection}
	Let $\Psi = \psi \cdot \mu^{1/2}$ be a time-dependent half density which satisfies the half-density advection equation
	\[
		\partial_t \Psi + \pounds_X [\Psi] = 0
	\]
	and let $\rho = \psi^\dagger \psi = \| \psi \|^2$.  Then $\rho$ satisfies the Louiville equaiton $\partial_t \rho + {\rm div}( \rho X ) = 0$.
	Conversely, if $\rho$ satisfies the Louiville equation, then there exists a half density $\Psi$ such that $\Psi^\dagger \Psi = \rho \cdot \mu$ and $\Psi$ satisfies the half-density advection equation.
\end{proposition}
\begin{proof}
	We see that $\rho \cdot \mu = \Psi^\dagger \cdot \Psi$.  Therefore $\pounds_X[ \rho \cdot \mu] = \pounds_X [\Psi^\dagger \cdot \Psi]$.
	We find
	\begin{align*}
		\pounds_X [\Psi^\dagger \cdot \Psi] &= \pounds_X[ \Psi^\dagger] \cdot \Psi + \Psi^\dagger \cdot \pounds_X [ \Psi ] \\
			&= (\pounds_X[ \psi^\dagger] + \frac{1}{2} \psi^{\dagger} {\rm div}(X) ) \psi \cdot \mu \\
			&\quad + \psi^\dagger ( \pounds_X[ \psi] + \frac{1}{2} \psi {\rm div}(X)) \cdot \mu \\
			&= (\pounds_X[ \psi^\dagger \psi] + \psi^\dagger \psi {\rm div}(X) ) \mu \\
			&= {\rm div}( \rho X) \mu.
	\end{align*}
	Therefore $\partial_t ( \rho \cdot \mu) + {\rm div}( \rho X) = 0$ and the proposition follows in one direction.  Conversely, let $\psi(x) = \sqrt{ \rho(x)}$, then we can verify directly that $\psi \cdot \sqrt{\mu}$ satisfies the half-density advection equation.
\end{proof}

While proposition \ref{prop:advection} allows us to advect smooth densities, one might be concerned that this does not fully communicate the dynamics.
The following proposition addresses this concern.

\begin{proposition} \label{prop:sanity_check}
	The advection equation $\partial_t \rho + \div(\rho \cdot X) = 0$ and the function ${\rm div}(X)$ contain the same information as the the vector field itself.
\end{proposition}
\begin{proof}
Let $\rho_\varepsilon$ be a sequence of functions which approaches a Dirac-Delta function as $\varepsilon \to 0$ centered at $x \in M$.
If $\rho_\varepsilon$ satisfies the advection equation, then by direct calculation we find
\[
	\lim_{\varepsilon \to 0} \langle \partial_t \rho_\varepsilon , f \rangle_{L^2} = \pounds_X[f] (x)+ {\rm div}(X)(x) f(x).
\]
Thus we may compute the Lie derivative of $f$ with respect to $X$ by computing the quantity $\langle \partial_t \rho_\varepsilon , f \rangle_L^2 - {\rm div}(X) f(x)$.
\end{proof}

\subsection{Discretization with half-densities}
Let $f_1, \dots, f_n$ be an orthonormal set of complex-valued functions on $M$.  Then $f_1 \sqrt{\mu} , \dots f_n \sqrt{\mu}$ are an orthonormal set of half-densities.  We can consider the $n \times n$-matrix
\[
	X_{j}^{i} = \langle f_i \sqrt{\mu} , \pounds_X [f_j \sqrt{\mu}]  \rangle.
\]
In normal coordinates
\[
	\pounds_X[ \psi \cdot \sqrt{\mu} ] = ( X^k(x) \partial_k \psi(x) + \frac{1}{2} \psi(x) \partial_k X^k(x) ) \sqrt{\mu}
\]
(see formula 13.3 of \cite{Meyer1998}) so that
\[
	X_j^i = \int_{M} ( X^k(x) \partial_k f_j(x) + \frac{1}{2} f_j(x) \partial_k X^k(x) ) f_i(x) \mu
\]
\begin{proposition}
	The matrix $X^i_j$ is anti-Hermitian.
\end{proposition}
\begin{proof}
	Let $\Psi_1$ and $\Psi_2$ be half densities.  As diffeomorphisms act unitarily on half-densities we find
	\[
		0 = \langle \pounds_X [\Psi_1^\dagger] , \Psi_2 \rangle + \langle \Psi_1^\dagger, \pounds_X[\Psi_2] \rangle
	\]
	In particular
	\begin{align*}
		X^i_j &= \langle f_i \sqrt{\mu} , \pounds_X [f_j \sqrt{\mu}]  \rangle \\
			&=  - \langle f_i \sqrt{\mu} , \pounds_X [f_j \sqrt{\mu}]  \rangle^\dagger \\
			&= -(X^j_i)^\dagger.
	\end{align*}
\end{proof}
Of course, the natural action of $\pounds_X$ on half-densities is a representation of the Lie algebra $\mathfrak{X}(M)$.
In this paper we will approximate this representation with the finite-dimensional matrix $X_j^i$ obtained from a wavelet basis.
Moreover, we will approximate the the flow of $\pounds_X$ with the matrix exponential.
