\documentclass[12pt]{amsart}
\usepackage{amsmath,amssymb}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry

%  POSSIBLY USEFULE PACKAGES
%\usepackage{graphicx}
%\usepackage{tensor}
%\usepackage{todonotes}

%  NEW COMMANDS
\newcommand{\pder}[2]{\ensuremath{\frac{ \partial #1}{\partial #2}}}
\newcommand{\ppder}[3]{\ensuremath{\frac{\partial^2 #1}{\partial
      #2 \partial #3} } }

%  NEW THEOREM ENVIRONMENTS
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{defn}[thm]{Definition}


%  MATH OPERATORS
\DeclareMathOperator{\Diff}{Diff}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\SO}{SO}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator{\supp}{supp}

%  TITLE, AUTHOR, DATE
\title{ROA as an LP}
\author{Henry O. Jacobs}
\date{\today}


\begin{document}

\maketitle

We consider the sequence of LP's

\begin{align*}
	p_{n,k}^* = \sup \int \rho_0 
\end{align*}
subject to the constraints
\begin{align*}
	&\rho \in V_n \\
	&\pounds[\rho]= 0 \\
	&\supp( \rho_T) \subset X_T \\
	&0 \leq \nabla^j \rho \leq \lambda \text{ for } j=0,\dots,k
\end{align*}
where $V_n$ is some $n$-dimensional subspace of $L^2$, probably consisting of hat functions
 and $\pounds[\rho] = \partial_t \rho + \sum_{j=1}^{n} \partial_j ( f^j \rho) $.  We need to use $L^2$ rather than $L^1$ because we need the domain to be a reflexive Banach space, in order to use the perturbation theorem of Reneger.
 If we replace $V_n$ with $H^k$ then we get an inner-approximation of the ROA\footnote{convergence to the full ROA?  Probably.  Lets put that aside for the moment.}.
 
Let $\nabla(V_n)$ denote the space induced by applying $\nabla$ to elements of $V_n$ (this might consist of indicator functions).
Let $\pi_n: L^1 \to \nabla(V_n)$ be some sort of projection such that $\| \pi_n(\rho) - \rho \|_{L^1}$ is bounded by $\mathcal{O}(F(n))$ for $\rho \in H^{k-1}$.
Then we can consider the perturbed problem
\begin{align*}
	\tilde{p}_{n,k}^* = \sup \int \rho_0 
\end{align*}
subject to the contraints
\begin{align*}
	&\rho \in V_n \\
	&\pi_n(\pounds[\rho])= 0 \\
	&\supp( \rho_T) \subset X_T \\
	&0 \leq \nabla^j \rho \leq \lambda \text{ for } j=0,\dots,k
\end{align*}

We've perturbed an operator in the contraint by an amount $\mathcal{O}(F(n))$ in the operator norm.
This perturbs the solution, $\rho$, by an amount $\mathcal{O}(F(n))$ in the operator norm on $C^1( [0,T], H^k(M) )$,
assuming these LPs are feasible.
We should choose $V_n$ and $\pi_n$ such that $F(n)$ is something like $\frac{1}{n^p}$ for some $p > 0$.

\appendix
\section{Sobelev theorems}
Let $\Omega \subset \mathbb{R}^n$ be bounded and l Lipschitz.
\begin{thm}
	The space $W^{k,p}(M)$ is compactly embedded in $W^{\ell,q}(M)$ when $k-\ell > 0$ and $k - \ell  > \frac{n}{p} - \frac{n}{q}$.
\end{thm}


\bibliographystyle{amsalpha}
\bibliography{hoj.bib}
\end{document}
